Kung Faux Pandas \\ \large Simplifying Privacy Protection

### 2018-06-01 paper/main.tex
Auto Update from local Sharelatex

Some text about Table~\ref{included-methods} including why we built the KDE method, why DataSynthesizer, and why SGF% Not sure where this table should go....

>>>>

KFP provides a framework by which any number of methods for data privacy can be carried out. For demonstration purposes we have implemented three plugins that use different techniques for data synthesis, as shown in Table~\ref{included-methods}. The kernel density estimator from scipy.stats.gaussian\_kde uses the method developed by Silverman \cite{silverman_density_1986} which handles inter-related ordinal and ratio data yet runs quickly on standard consumer level hardware. The DataSynthesizer method, created by Ping et al. \cite{ping17datasynthesizer} is built on differential privacy mechanisms and has multiple internal methods for data generation ranging from random generation based on data type to Bayesian modeling of inter-relationships among columns of data. Lastly, the Synthetic dataset Generation Framework by Bindschaedler et al. \cite{Bindschaedler2017} has ma

Bindschaedler - shows synthetic data are close enough that models built with synthetic data are simlar to model built with real data.
? Ping?

### 2018-06-01 paper/seth.tex
Auto Update from local Sharelatex

 techniques for privacy protection:
 * De-identifcation
   * removal of known unique identifiers
   * Data summarization to prevent individual identification
 * Synthesis - Generating data based on some statistical model

>>>>

 techniques for privacy protection:
 * De-identifcation
   * removal of known unique identifiers
   * Data summarization to prevent individual identification
   * Problem: "Although these techniques support privacy protected data publishing without synthesis, the degree of privacy protection they provide depends on the background knowledge of adversaries."
 * Synthesis - Generating data based on some statistical model; "...the process of creating artificial data that can be used to serve some key purposes of real data."
